Co-moving stars in \textsl{Gaia DR1}

### 2016-11-17 paper/ms.tex
Fix typo

At small separations ($0.001-1$~pc), they are wide binaries (and
multiples) that are either weakly gravitationally bound or
slowly separating.
Because they have low binding energies, a sample of wide binaries is valuable
for investigating the Galactic dynamical environment.
These systems must have survived both their dynamic birth environment and 
have avoided tidal destruction along their orbit.
Thus, the statistical properties of wide binaries provide a window into both the star formation
process and the Galactic dynamics
including Galactic tides, and other massive perturbers such as molecular clouds
and MACHOs \citep{Yoo:2004aa,Allen:2014aa}.
Wide binaries are also good testbeds for stellar evolution models.
For example, main sequence-red giant wide binaries are especially valuable in
testing consistency between stellar atmosphere models as the
two stars were likely born at the same time with the same chemical compositions,
but evolved indepdently because of their wide separation.
Finally, calibration of stellar parameters of low-mass stars (e.g., M dwarfs),
which dominate the stellar content of the Galaxy by number, can benefit from
a larger sample of widely separated binaries containing a low mass star and a
much brighter FGK star whose stellar parameters are easier to measure
\citep[e.g.,][]{Rojas-Ayala:2012aa}.

>>>>

At small separations ($0.001-1$~pc), they are wide binaries (and
multiples) that are either weakly gravitationally bound or
slowly separating.
Because they have low binding energies, a sample of wide binaries is valuable
for investigating the Galactic dynamical environment.
These systems must have survived both their dynamic birth environment and 
have avoided tidal destruction along their orbit.
Thus, the statistical properties of wide binaries provide a window into both the star formation
process and the Galactic dynamics
including Galactic tides, and other massive perturbers such as molecular clouds
and MACHOs \citep{Yoo:2004aa,Allen:2014aa}.
Wide binaries are also good testbeds for stellar evolution models.
For example, main sequence-red giant wide binaries are especially valuable in
testing consistency between stellar atmosphere models as the
two stars were likely born at the same time with the same chemical compositions,
but evolved independently because of their wide separation.
Finally, calibration of stellar parameters of low-mass stars (e.g., M dwarfs),
which dominate the stellar content of the Galaxy by number, can benefit from
a larger sample of widely separated binaries containing a low mass star and a
much brighter FGK star whose stellar parameters are easier to measure
\citep[e.g.,][]{Rojas-Ayala:2012aa}.
